\thesistitle

### 2019-08-25 sections/conclusion.tex
Background again
Conclusion

\subsection{Survey}
To limit the scope of this research, we chose not to include human subjects in this study. However, we think that the results of this study could be strengthened by performing a survey on software engineering practitioners. We have determined a set of refactoring opportunities only based on literature input and quantitive analysis. It would be valuable to have a control group rate the refactorings performed by CloneRefactor, as an extra form of input regarding the quality of the code transformation that CloneRefactor performs.

@@

\subsection{Automated Refactoring for more metrics}
In this study, we presented evidence regarding the value of applying automated refactoring to analyze the before- and after state of refactored source code. Analyzing these states we were able to analyze the improvement in maintainability after refactoring duplicated code. This allows us to better assess thresholds by which maintainability issues in source code are identified. We also get better insights into the costs and values of applying certain refactoring efforts.

@@

If a method has many parameters, we can group strongly related parameters into an object. This can be done automatically, but two things must be considered:
\begin{itemize}
  \item How do we determine whether parameters are strongly related?
  \item At what other places is this data used in unison and should thus use the new abstraction?
\end{itemize}
To determine whether parameters are strongly related we must look into at what places they are used in the codebase. We must then define some threshold that denotes the percentage of usages of these variables in which they are used together. If this threshold exceeds a certain amount, we can group them into an object. We must then trace all the places in which they are used together and replace the variables by the newly created abstractions. If long parameter lists can be automatically refactored, automated clone refactoring can be improved by automatically grouping data into objects if they are used in unison.

@@

Refactoring complex/large methods can largely be done automatically by applying ``Extract Method'' to large methods. Also, many of the results of this study can be reused. To assess an automated refactoring opportunity for complex methods, we should assess which parts of methods can be split to end up with parts of similar complexity. For this, our research can be used to assess whether a given piece of code can be extracted to a new method (see Section~\ref{sec:refactorabilitysetup}).

@@

\subsection{Type 4 clones}
Type 4 clones are defined as \textit{two or more code fragments that perform the same computation but implemented through different syntactic variants.} \cite{roy2007survey}. We think that there are relevant research opportunities in refactoring type 4 clones. Type 4 clones are functionally equal pieces of code that are implemented through different implementations. Although functionally equal, type 4 clones might still differ in other aspects. For instance, for type 4 clones, one alternative might be easier to maintain. Also, they can differ in performance.

There are interesting research opportunities in automatically choosing the better alternative among type 4 clone instances.

@@

\subsection{Naming of refactored methods/classes/etc.}
In this study, we took the naming of refactored entities out of the scope. We applied automated refactoring to duplication and gave all generated methods, classes and interfaces generated names. For our purposes that was not much of an issue, because of the validation methods used. We validated our approach using the SIG Maintainability model, which does not take naming quality into account. Because of that, the results of our experiments are in no way dependent on the names we give the generated methods, classes and interfaces.

When using our work for refactoring assistance, these names will have to be manually provided. However, recent studies allow assistance in this process by generating a name that matches the body of a declaration. If this can be done reliably, we can apply refactorings without any manual steps required.

A study by Allamanis et al. \cite{allamanis2015suggesting} proposes a machine learning model that can suggest accurate method and class names. This study shows promising results towards generating method and class names based on their body and context. However, the source code of this study is not available, making it harder to apply their findings to generate class and method names for any software project.

In a recent study by Alon et al. \cite{alon2018code2seq} they propose code2seq. Code2seq is a machine learning model that guesses the name of a method given a method body. This model has been trained on a large set of method bodies and names. The model already shows promising results. The source code of code2seq is publicly available, making it possible to embed this model in any application. Although this model is still far from perfect, combining it with our research could already greatly reduce the manual refactoring effort required. The main deficiency of this model lies in that it's limited to the method body and does currently not consider anything else in a method body. This method is flawed because the meaning of method bodies depends heavily on their context. For instance, the body of the method \texttt{get()} in \texttt{ArrayList} does not make any sense in relation to its name without considering its context (class, inheritance hierarchy, etc.).

\subsection{Looking into other languages/paradigms}
In this study, we describe duplicate code refactoring opportunities for object-oriented languages. We built a tool to refactor code clones in Java and used it to run our experiments.

@@

In this study, we focused only on the object-oriented paradigm because of the shared concepts. However, the problems that come with duplication in source code also appears in different programming languages. Because of that, more insights could be obtained when looking into automated refactoring opportunities for other paradigms. For instance, it might be valuable to look into opportunities to reduce duplication in the functional domain. Dealing with code clones in the functional paradigm is largely an unexplored field and might hold valuable results.

\subsection{Automatically refactoring code that is duplicated with a library}
One of the clone detection tools we analyzed in this study is Sisyphus \cite{eremondi2017sisyphus}. This clone detection tool searches a codebase for methods that are part of the Java standard libraries. There are definite automated refactoring opportunities here, automatically switching to the library implementation if available. This doesn't have to be limited to just the Java standard library., it is also possible to search the external libraries the project uses.

>>>>

\subsection{Survey}
To limit the scope of this research, we chose not to include human subjects in this study. However, we think that the results of this study could be strengthened by performing a survey on software engineering practitioners. We have determined maintainability scores only based on literature input and statistical analysis. It would be valuable to have a control group rate the refactorings performed by CloneRefactor, as an extra form of input regarding the quality of the code transformations that CloneRefactor performs.

@@

\subsection{Automated Refactoring for more metrics}
In this study, we apply automated refactoring to analyze the before- and after state of refactored source code. This allows us to better determine which thresholds identify problems that should be refactored.

@@

To refactor a method with many parameters, one should group strongly related parameters into an object. This can be done automatically, but two things must be considered:
\begin{itemize}
  \item How do we determine whether parameters are strongly related?
  \item At what other places is this data used in unison and should thus use the new abstraction?
\end{itemize}
To determine whether parameters are strongly related we must look into at what places they are used in the codebase. We must then define some threshold that denotes the percentage of usages of these variables in which they are used together. If this threshold exceeds a certain amount, we can group them into an object. We must then trace all the places in which they are used together and replace the variables by the newly created abstractions. If long parameter lists can be automatically refactored, automated clone refactoring can be improved by automatically grouping data if the extracted method requires many parameters.

@@

Refactoring complex/large methods can largely be done automatically by applying ``Extract Method'' to large methods. Many of the results of this study can be reused. To assess an automated refactoring opportunity for complex methods, we should assess which parts of methods can be split to end up with parts of similar complexity. For this, our research can be used to assess whether a given piece of code can be extracted to a new method (see Section~\ref{sec:refactorabilitysetup}).

@@

\subsection{Type 4 clones}
Type 4 clones are defined as \textit{two or more code fragments that perform the same computation but implemented through different syntactic variants.} \cite{roy2007survey}. We think that there are relevant research opportunities in refactoring type 4 clones. Although type 4 clone instances perform the same computation, they may still differ in other aspects. For instance, one alternative might be easier to maintain or have a better performance. There are interesting research opportunities in automatically choosing the better alternative among type 4 clone instances.

@@

\subsection{Naming of refactored methods/classes/etc.}
In this study, we applied automated refactoring to duplication and gave all generated methods, classes and interfaces generated names. For our purposes that was not much of an issue, because we used a maintainability model \cite{heitlager2007practical} that does not take naming quality into account. Because of that, the results of our experiments are not dependent on the names we give the generated declarations.

When using our work for refactoring assistance, these names will have to be manually provided. However, recent studies allow assistance in this process by generating a name that matches the body of a declaration. If this can be done reliably, it is possible to apply automated refactorings without any manual steps required.

A study by Allamanis et al. \cite{allamanis2015suggesting} proposes a machine learning model that can suggest accurate method and class names. This study shows promising results towards generating method and class names based on their body and context. However, the source code of this study is not available, making it harder to apply their findings.

In a recent study by Alon et al. \cite{alon2018code2seq} the authors propose code2seq. Code2seq is a machine learning model that guesses the name of a method given a method body. This model has been trained on a large set of method bodies and names. The model already shows promising results. The source code of code2seq is publicly available, making it possible to embed this model in any application. Although this model is still far from perfect, combining it with our research could already greatly reduce the manual refactoring effort required. The main deficiency of this model lies in that it only guesses the name on basis of the body of the method and not its context. %This method is flawed because the meaning of method bodies depends heavily on their context. For instance, the body of the method \texttt{get()} in \texttt{ArrayList} does not make any sense in relation to its name without considering its context (class, inheritance hierarchy, etc.).

\subsection{Looking into other languages}
In this study, we describe duplicate code refactoring opportunities for object-oriented languages. We built a tool to refactor code clones in Java and used it to run our experiments.

@@

%\subsection{Automatically refactoring code that is duplicated with a library}
%One of the clone detection tools we analyzed in this study is Sisyphus \cite{eremondi2017sisyphus}. This clone detection tool searches a codebase for methods that are part of the Java standard libraries. There are definite automated refactoring opportunities here, automatically switching to the library implementation if available. This doesn't have to be limited to just the Java standard library, it is also possible to search the external libraries the project uses.
